The Forward March of Categorical Tolerance in the United States\thanks{Reserved for acknowledgments}

### 2025-11-14 analysis-comp.qmd
oof

```{r setup, include=FALSE}
     knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
     library(conflicted)
     library(haven)
     library(here)
     library(dplyr)
     library(tidyr)
     library(qualtRics)
     library(ggplot2)
     library(pscl)
     conflicts_prefer(dplyr::filter)
     conflicts_prefer(dplyr::select)
     conflicts_prefer(dplyr::summarize)
     source(here("Functions", "dat.genres.R"))
```

@@

```{r Zero Inflated Regression}
    dat.dis.12$sample = "2012"
    dat.dis.25$sample = "2025"
    dat.dis$sample = "2021/23/25"
    pooled.dat <- rbind(dat.dis.25, dat.dis.12)
    pooled.dat$sample <- factor(pooled.dat$sample)
    m1 <- zeroinfl(num.dis ~ sample | sample, data = pooled.dat)
    summary(m1)
    tab_model(m1, transform = NULL, digits = 3, prefix.labels = "none",
            file = here("Tabs", "zinf-reg-comp.html"), 
            auto.label = TRUE, dv.labels = c("Model 1"), 
            CSS = list(css.table = 'font-size: 12px;', css.td = 'border-bottom: 0px;'), 
            show.zeroinf = TRUE, show.ci = FALSE,
            pred.labels = c("Intercept", "Sample (2025)")
            )
```

```{r}
    library(ggeffects)
    pv <- predict_response(m1, "sample", type = "zi_prob")
    p <- plot(pv, ci_style = "errorbar", dot_size = 5.5)
    p <- p + theme_minimal()
    p <- p + theme(axis.text = element_text(size = 18),
                    axis.title = element_blank(),
                    plot.title =  element_text(size = 24)
                    )
    p <- p + ggtitle("Predicted Zero-Inflation Probabilities")
    p
    save_plot(here("Plots", "zip-pred-comp.png"), height = 20, width = 15)
```

>>>>

```{r setup, include=FALSE}
     knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
     library(conflicted)
     library(here)
     library(dplyr)
     library(tidyr)
     library(webshot)
     library(qualtRics)
     library(kableExtra)
     library(ggplot2)
     library(ggeffects)
     library(sjPlot)
     library(pscl)
     library(haven)
     conflicts_prefer(dplyr::filter)
     conflicts_prefer(dplyr::select)
     conflicts_prefer(dplyr::summarize)
     source(here("Functions", "dat.genres.R"))
```

@@

```{r Zero Inflated Regression}
    dat.dis.12$sample = "2012"
    dat.dis.25$sample = "2025"
    dat.dis$sample = "2021/23/25"
    pooled.dat <- rbind(dat.dis.25, dat.dis.12)
    pooled.dat$sample <- factor(pooled.dat$sample)
    m1 <- zeroinfl(num.dis ~ sample | sample, data = pooled.dat)
    summary(m1)
    tab_model(m1, transform = NULL, digits = 3, prefix.labels = "none",
            file = here("Tabs", "zinf-reg-comp.html"), 
            auto.label = TRUE, dv.labels = c("Model 1"), 
            CSS = list(css.table = 'font-size: 12px;', css.td = 'border-bottom: 0px;'), 
            show.zeroinf = TRUE, show.ci = FALSE,
            pred.labels = c("Intercept", "Sample (2025)")
            )
    webshot(here("Tabs", "zinf-reg-comp.html"), here("Tabs", "zinf-reg-comp.png"), zoom = 4)
```

```{r Predicted Probabilities}
    pv <- predict_response(m1, "sample", type = "zi_prob")
    p <- plot(pv, ci_style = "errorbar", dot_size = 5.5)
    p <- p + theme_minimal()
    p <- p + theme(axis.text = element_text(size = 18),
                    axis.title = element_blank(),
                    plot.title =  element_text(size = 24)
                    )
    p <- p + ggtitle("Predicted Zero-Inflation Probabilities")
    p
    save_plot(here("Plots", "zip-pred-comp.png"), height = 20, width = 15)
```
